Bioverse: Potentially Observable Exoplanet Biosignature Patterns Under the UV Threshold Hypothesis for the Origin of Life

### 2025-03-11 src/tex/ms.tex
change wording

\rev{If the rate of life’s emergence and persistence $f_\mathrm{life}$ is at a \SI{1}{\percent} level or lower, no currently planned exoplanet mission concept has projected sample sizes sufficient to test the UV~Threshold Hypothesis.
One } exception is the Nautilus Space Observatory concept~\citep{Apai2019,Apai2022}.
Nautilus aims to characterize up to $\sim 1000$ \gls{EEC} via transmission spectroscopy, building on an innovative optical technology.
To guide the definition of future biosignature surveys, it is important to refine predictions on the role of \gls{UV} radiation in prebiotic chemistry with both theoretical and experimental work.

>>>>

\rev{If the rate of life’s emergence and persistence $f_\mathrm{life}$ is at a \SI{1}{\percent} level or lower, no currently envisioned future exoplanet mission has projected sample sizes sufficient to test the UV~Threshold Hypothesis.
One possible} exception is the Nautilus Space Observatory concept~\citep{Apai2019,Apai2022}.
Nautilus aims to characterize up to $\sim 1000$ \gls{EEC} via transmission spectroscopy, building on an innovative optical technology.
To guide the definition of future biosignature surveys, it is important to refine predictions on the role of \gls{UV} radiation in prebiotic chemistry with both theoretical and experimental work.
